### 2012-11-27 inst/examples/policycosts/L2.Rmd
minor changes, housekeeping

``` {r setup, include=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width=5, height=5) pdf(NULL, width = width, height = height))
````

>>>>

``` {r setup, include=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"))
theme_update(plot.background = element_rect(fill = "transparent",colour = NA))
options(device = function(width=5, height=5) pdf(NULL, width = width, height = height))
````
